Optical characterization of gaps in directly bonded Si compound optics using infrared spectroscopy

### 2015-03-24 AO_bondedSi.tex
spruce up the discussion section to be more general from a reader point of view

\subsection{Questioning assumptions of the model}

\emph{More complex underlying gap size distributions-} One key assumption of our model is that the distribution of gap sizes over our measurement area is bimodal.  Specifically, Equation \ref{eqnMix} assumes that there is either a gap of size $d$, or else it is 100\% bonded.  If there is a gradient across the bond, the emergent transmission spectrum will be an admixture of many gaps with various areal coverage fractions.  The full solution becomes an areal integral of Equation \ref{eqFP} normalized by the total measurement area.  Solving for the relative distributions of gaps is highly degenerate, in the same way as we saw in the 2-parameter corner plots of gap depth and fill factor.  We experimented with by-eye fitting parametric distributions of gap sizes, characterized by a maximum and minimum gap size, and a monotonic slope of the distribution.  We found that measurements of very large ($>10\lambda$) gaps with a large gradient offered surprisingly strong constraints on the maximum gap size, because of the conspicuous high frequency Fabry-P\`erot fringes.  For sub-wavelength gaps, the gap size distibution is too degenerate to derive much useful insight on the slope of the distribution.  Specifically, for $d_{max}<\lambda/4$, our simple mixture model will converge on the spectrum of the average gap size, even if the \emph{True} distribution is more complex.  Reducing the measurement area could break some of these degeneracies, if more precision is desired.

\emph{Origin and properties of correlated noise- } Another key assumption of our analysis is that correlated errors dominate the measurement uncertainty.  We have assumed that the Gaussian process can capture the effect of the observed correlated errors.  We tested the need for Gaussian process regression by generating synthetic data spectra with known gap size and fill factor, and known covariance structure.  We applied ordinary least squares regression to the synthetic spectra and derived values for $d$ and $f$ that were biased by up to $20\sigma$ or more.  Applying Gaussian process regression recovered the input values to within $1\sigma$.

@@

\emph{DSP vs AR coated front faces- } Another key assumption of the model is that all the Si$-$air interfaces are well-approximated by Fresnel reflection losses.  If the entrance and exit faces of the bonded samples are AR coated, the incoherent multiple reflection model will have to be modified.  AR coated front and exit faces will result in a larger interface loss for a given gap size than the interface loss computed here.

\emph{Refactive index- } We have assumed that the refractive index is identical to that given by \cite{2006SPIE.6273E..77F}.  Double beam mode measurements can reach a precision of comparable to the part-to-part variation of refractive index.  We have attempted to normalize spectra by their singleton counterparts when possible.  We do not present measurements made with double beam mode in this article.

\emph{Diffraction from mesh patterns}
It's conceivable that the edges of the mesh patterns diffract or scatter the beam (Figure \ref{figVS20pattern}).  We ruled out wavelength-dependent diffraction from the mesh pattern as a measurement artifact, since the beam size is large and the angular spread of diffraction from the mesh pattern would be much smaller than the spread of the beam.  To eliminate this concern, we measured in the coarse mesh rather than the medium or fine meshes, when possible.  We saw no difference in the bond quality surrounding the medium or fine meshes, which is consistent with results from the literature \cite{1992JEMat..21..669M}.  Specifically, the gas pressure of bonded wafers grows as the fill factor of gaps decreased.  In other words, what matters is the fill factor of gaps, not their relative sizes.  Since the fine, medium, and coarse meshes had the same fill factors, we anticipate no difference in the pressure of the gaps, and therefore no difference in the bonding properties.

>>>>

The experiments and measurements in Section \ref{secResults} demonstrate that we can detect and measure the axial extent of gaps down to 14 nm.  The technique is \emph{non-destructive} and can be implemented with an off-the-shelf comercial product, namely the Cary 5000 or equivalent, or any existing high precision spectrograph.  The spectrograph need not be high resolution-- our 5 nm spectral resolution was not a limiting factor.  The limiting factor is spectrophotometric \emph{accuracy} and \emph{precision}.  In this Section we question the assumptions of our technique, identify its limitations, and mention some opportunities.

\emph{More complex underlying gap size distributions-} One key assumption of our gap-as-etalon modeling strategy is that the distribution of gap sizes over the measurement area is bimodal- a gap of size $d$ or zero gap.  This choice was simply a matter of computational simplicity, and any more complicated gap size distribution could easily be dropped in as additional terms in Equation \ref{eqnMix}.  For example, if there is a gradient across the bond, the emergent transmission spectrum will be an admixture of many gaps with various areal coverage fractions.  The full solution becomes an areal integral of Equation \ref{eqFP} normalized by the total measurement area.  Solving for the relative distributions of gaps is highly degenerate, in the same way as we saw in the 2-parameter corner plots of gap depth and fill factor.  We experimented with by-eye fitting parametric distributions of gap sizes, characterized by a maximum and minimum gap size, and a monotonic slope of the distribution.  We found that measurements of very large ($>10\lambda$) gaps with a large gradient offered surprisingly strong constraints on the maximum gap size, because of the conspicuous high frequency Fabry-P\`erot fringes.  For sub-wavelength gaps, the gap size distibution is too degenerate to derive much useful insight on the slope of the distribution.  Specifically, for $d_{max}<\lambda/4$, our simple mixture model will converge on the spectrum of the average gap size, even if the \emph{True} distribution is more complex.  Reducing the measurement area could break some of these degeneracies, if more precision is desired.

\emph{The benefit of the Gaussian process-} We chose to estimate the gap size with a Gaussian process regression, but this is not necessary.  Any model fitting strategy, like least squares or overplotting a model to data by-hand, will yield an estimate for a gap size.  We tested the benefit of Gaussian process regression by generating synthetic data spectra with known gap size and fill factor, and known covariance structure.  We applied ordinary least squares regression to the synthetic spectra and derived values for $d$ and $f$ that were biased by up to $20\sigma$ or more.  Applying Gaussian process regression recovered the input values to within $1\sigma$.

@@

\emph{DSP vs AR coated front faces- } We have assumed that the Si$-$air interfaces are approximated by Fresnel reflection losses.  If the entrance and exit faces of the bonded samples are AR coated, the incoherent multiple reflection model will have to be modified.  AR coated front and exit faces will result in a larger interface loss for a given gap size than the interface loss computed here.

\emph{How far can this technique go?}  The spectrophotometric precision of our instrument flows down directly to limit the smallest measureable gap size.  This limitation will vary from instrument to instrument.  Our instrument can achieve 10 times better accuracy and precision in double beam mode.  However, the slightly different polarization sensitivity in the different beams caused systematic jumps at the lamp/grating change-over wavelengths.  Agilent offers an adaptor to reduce the polarization sensitivity, which mitigates these lamp jumps.  If precisions of 0.02\% could be achieved, gaps $<4$ nm could be reliably measured.  This level begins to be comparable to the effect of interesting physics, like surface roughness and refractive index.  In fact, the van der Waals bond energy could be constrained from these types of measurements \cite{2001JOptA...3...85G}.

\emph{Can this technique be applied to imaging?}  The analysis performed in this article informs smart strategies for using IR imaging for gap detection in bonded Si optics.  First, Equation \ref{eqFP} shows that short wavelengths have the most discerning power for detecting small gaps.  So an IR imaging approach should use the shortest possible wavelength without getting close to the Si absorption cutoff.  This work recommends a 1250$-$1300 nm filter.  Images can then be normalized to the transmission through a DSP sample under identical, nearly collimated lighting conditions.  Lastly, any deficits in flux of a bonded sample can be converted to a gap size $d$, using Equation \ref{eqFP}.  IR imaging will lack the spectral information available in the spectra shown in this article.  The imaging will require exceptional quality of flat-fielding or dithering of the images to reach the precision achieved here with relative ease.
